Hydras \& Co.

### 2022-03-19 doc/part-hydras.tex
corrections chapter 6 (completed)

\begin{remark}
The difference with the ``classic'' Wainer hierarchy 
$f\_\alpha\;(\alpha<\epsilon_0)$ lies in the second equation:
$f_{\beta+1}(i) = (f_\beta)^{(i)}(i)$ and not
$f_{\beta+1}(i) = (f_\beta)^{(i+1)}(i)$.

@@

A first attempt is to write a definition of $F_\alpha$ by equations, in the same way as for $H\_alpha$ (the functional \texttt{iterate} has already been used in Sect.\vref{Functions:iterate}).

@@

Prove that for any $n\geq 2$, $\textrm{Ack}\,\,n\,n\leq  F_\omega(n)$, where \textrm{Ack} is the Ackermann function. Next, prove that $F_\alpha$ is not primitive recursive, for any $\alpha\geq\omega$  (please see Sect.~\vref{sect:ack-not-PR}).
On the other hand, please show that for any natural number $n$, the function $F_n$ is primitive recursive.
Thus $F\_alpha$ is primitive recursive if and only if $\alpha$ is finite.

@@

>>>>

\begin{remark}
The difference with the ``classic'' Wainer hierarchy 
$f_\alpha\;(\alpha<\epsilon_0)$ lies in the second equation:
$f_{\beta+1}(i) = (f_\beta)^{(i)}(i)$ and not
$f_{\beta+1}(i) = (f_\beta)^{(i+1)}(i)$.

@@

A first attempt is to write a definition of $F_\alpha$ by equations, in the same way as for $H_\alpha$ (the functional \texttt{iterate} has already been used in Sect.\vref{Functions:iterate}).

@@

Prove that for any $n\geq 2$, $\textrm{Ack}\,\,n\,n\leq  F_\omega(n)$, where \textrm{Ack} is the Ackermann function. Next, prove that $F_\alpha$ is not primitive recursive, for any $\alpha\geq\omega$  (please see Sect.~\vref{sect:ack-not-PR}).
On the other hand, please show that for any natural number $n$, the function $F_n$ is primitive recursive.
Thus $F_\alpha$ is primitive recursive if and only if $\alpha$ is finite.

@@

\paragraph*{\gaiasign} Library~\href{../theories/html/gaia_hydras.GF_alpha.html}{gaia\_hydras.GF\_alpha}  defines the functions $F_\alpha$ for \gaia's world.
